Analysis of Security-Cost Trade-off of Fully Homomorphic Encryption Schemes

### 2013-06-16 Report/article.tex

\subsection{Intial set-up cost}
Here we mesure the performance in terms of run time for KeyGen, Encrypt, Add, Mult, Recrypt, Decrypt.\\
\begin{tabular}{|c|c|c|c|c|c|c|c|}
  \hline
  \multicolumn{8}{|c|}{$\mu = 4$} \\
  \hline
  N & $log_{2}(p)$ & KeyGen & Encrypt & Add & Mult & Recrypt & Decrypt \\
  \hline
  $2^{1}$ & 1.2 & & 1.3 & & & & \\
  $2^{2}$ & 2.2 & & 2.3 & & & & \\
  $2^{3}$ & 2.2 & & 2.3 & & & & \\
  $2^{4}$ & 2.2 & & 2.3 & & & & \\
  $2^{5}$ & 2.2 & & 2.3 & & & & \\
  \hline
\end{tabular}

\textbf{KeyGen}\\
The measured time execution for KeyGen($N, \mu$)  for fixed values of parameters: $N=8$ and $\mu = 4$ show a variation from 0.2 s to 14.41 s with big density at the interval [0.2s, 2s]\autoref{image_f2}.

\begin{figure}[!h] %on ouvre l'environnement figure
\centering
\includegraphics[width=5cm]{f3.pdf} 
\caption{Run time of KeyGen(ms)} 
\label{image_f2} %l'étiquette pour faire référence à cette image
\end{figure}

@@

\section{Experimental evaluation \\ and analysis}
\label{Sec:Eval}
Measurements by varying the parameters or the plaintext size.

>>>>

\subsection{Intial set-up cost}
Here we mesure the performance in terms of run time for KeyGen, Encrypt, Add, Mult, Recrypt, Decrypt.\\
\begin{table}[htb]
  \centering
  \caption{Run time (ms)}
\resizebox{9 cm}{!}{
\begin{tabular}{|c|c|c|c|c|c|c|c|}
  \hline
  \multicolumn{8}{|c|}{$\mu = 4$ , $\eta = 2^{384}$} \\
  \hline
  $N=2^{n}$ & $log_{2}(p)$ & KeyGen & Encrypt & Add & Mult & Recrypt & Decrypt \\
  \hline
  $2^{1}$ & 764 & 99 & 0.057 & 0.0 & 2.372 & 2.371 & 0.0 \\
  $2^{2}$ & 1535 & 221 & 0.072 & 0.0 & 	3.012 & 3.023 & 0.001\\
  $2^{3}$ & 3077 & 1131 & 0.079 & 0.001 & 3.396 & 3.380 & 0.004 \\
  $2^{4}$ & 6155 & 8560 & 0.135 & 0.002 & 5.881 & 5.889 & 0.012\\
  $2^{5}$ & 12329 & 852849 & 0.477 & 0.005 & 20.230 & 20.057 & 0.028\\
  \hline
\end{tabular}
\normalsize
\label{common cost}
}
\end{table}

\textbf{KeyGen}\\
The measured time execution for KeyGen($N, \mu$)  for fixed values of parameters: $N=8$ and $\mu = 4$ show a variation from 0.2 s to 14.41 s with big density at the interval [0.2s, 2s]\autoref{fig:image_f2}.

\begin{figure}[!h] %on ouvre l'environnement figure
\centering
\includegraphics[width=5cm]{f3.pdf} 
\caption{Run time of KeyGen(ms)} 
\label{fig:image_f2} %l'étiquette pour faire référence à cette image
\end{figure}

@@

\section{Experimental evaluation and analysis}
\label{Sec:Eval}
Measurements by varying the parameters or the plaintext size.
